### 2025-05-08 manuscript/manuscript.Rmd
Adding MAA results

@@

>>>>

Same basic pattern in the evening except MAAs, guanosine, proline?

Deep labeling is slower and much more limited for ammonia

  - Asp/Asn especially
  - Ectoine major exception (ref mcparland for bacterial signal)

Nitrate surface morning surprisingly limited

  - "out of order" labeling in MAAs and guanine, maybe also arginine, taurine, NAc-lysine, maybe maybe theanine being unlabeled because it would mean diatoms don’t make it

Organic compounds equally bioavailable at surface and deep and used very similarly to each other

  - Exceptions: guanosine (not guanine!) for GMP amendments
  - Exceptions: arginine, citrulline, maybe ornithine for Arg (signal goes away after a while and unclear why??)

Organics seem to be largely used for ammonia rather than as-is

  - Carbon backbone traced into glutamate from arginine
  - Carbon backbone traced into other nucleobases from GMP
  - Possibly due to way too much of a given compound, useless to have that much Arg/GMP
  - Not very much fully-labeled guanine despite guanosine being easily cleavable, instead it’s mostly made from scratch (CHECK THIS)
  - Creatine for being mostly 2x15N 1x13C labeled from arginine

@@

Untargeted metabolites? Clustering their % labeled patterns with the targeted metabolites to see what groups they might belong to
